\documentclass{article}
\usepackage{setspace} 
\usepackage{multicol}
\usepackage{geometry}
\usepackage{pythontex}

\geometry{a4paper}
\geometry{left=2cm,right=2cm,top=2cm,bottom=2cm} 
\pagestyle{empty}
\begin{document}
\title{Guinea Pig Rule}
\maketitle


\begin{multicols}{2}

\begin{enumerate}
\item Keep quiet and don't talk to me.
\item Piglets are not allowed to eat adult food.
\item Dream about getting a good carrot.
\item Foolish children are not allowed to play.
\item Boggy stay in the house.
\item Help your friends.
\item Walk around the house.
\item No one is allowed to play in the living room.
\item No one is allowed to play in the kitchen.
\item No one is allowed to play in the bedroom.
\item No one is allowed to play in the bathroom.
\item Crying is not allowed, but saying "I'm sorry" is.
\item Say "I'm sorry" when you are sad.
\item Scream when you are in trouble.
\item Take pictures of your friends.
\item Don't bit your friends.
\item Call your parents when you are in trouble.
\item Learn to play the piano.
\item Practice your French.
\item Math is fun.
\item Sleep before 10 p.m.
\item Run around the house at least once a day.
\item Slip on your slippers but don't fall.
\item Swim in the pool not in the pond.
\item Speak in the living room not in the bedroom.
\item Chat by phone not in the bedroom.
\item iPad must close before 10 p.m.
\item Ride horse in the field not in the school.
\item Go to school in time. 
\item Emily's birthday is on the third day of the month.
\item Emily's breakfast gone for good for mysterious reasons.
\item Guinea pigs are not narcissists. 
\item Guinea pigs are not from the guinea. So do not be silly, you are not got a home sick.
\item Your are sick because you are hungry.
\item Because of your bad attitude, you are not able to join the party.
\item e-mail is not allowed.
\item Sigh when you are sad.
\item Wipe your tears and you will be happy.
\item You are not allowed to have children until you are old enough.
\item Chat with your piglets. Teach them how to talk.
\item Hamsters are evil. Do not play with them. When they come, they will eat you.
\item Cats are danger. Do not let them in. 
\item Chicken is good. But they are not allowed to eat children.
\item Grass is the best. Carrot is good too. but Hamsters are evil.
\item Eat grass not carrot.
\item Dive into the water is illegal for the piglets.
\item Do Not break the guinea pig rule. 
\item Keep an eye on your piglets. Feed them well. Treat them well. 
\item Flying for guinea pigs are dangerous, do it only when you are in the house. 
\item Go out regularly.
\item Beware the tortoise.
\item Be easy to find.
\item Don't eat my food.
\item Don't chew your house. 
\item Jumping is not allowed.
\item Bitting piglets is not allowed.
\item Have a dose vitamin C a day.
\item Chew a cuttlebone each month.
\item Brush your teeth twice a day.
\item Bath more than once a day.
\item Give your children good bath as more as you can.  
\item Be good to each other.
\item Keep it clean.
\item Fight for your rights.
\item Care of the environment.
\item Stay safe.
\item Be responsible.
\item Try to be a good pet.
\item Stay away from children.
\item Home is where you are.
\item Some say that you are a guinea pig. It is true.
\item I'm serious. you are a guinea pig.
\item Care your family.
\item Male is not allowed here. 
\item Learn to speak like a human.
\item Think before you write. 
\item Home sweet home.
\end{enumerate}
\end{multicols}
\end{document}